Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-09 chi2013-webbox.tex
mum edits ps

All of the participants used multiple web sites in order to complete their tasks, and all felt that the lack of existing integration between sites hindered their ability to make informed choices. Participants prioritised the sources they used by both the ease and immediacy of accessing them.  Conversely, sources that took much effort or time to investigate were often excluded.

@@

\subsection{PS.2 - Technical Challenges of Data Integration}
Our analysis of structured data feeds started with identifying a set of candidate sources to examine.  We consulted the ProgrammableWeb API directory\footnote{ProgrammableWeb: \url{http://www.programmableweb.com/apis/directory}} list of most popular data feeds for this purpose.  To increase the variety of sources, we selected from 5 categories: social network services, retailers, online event calendars, music sites, and weather, selecting 2--5 sources from each, for a total of 20.

For each feed, 3--5 typical records of a particular type were obtained from each service's API or feed.  For social networking sites, user profiles were the type of record examined, while for retail sites, event tracking sites, music sites and weather sites, product information, event time/date info, song listing information, and weather forecasts were examined, respectively.
%Records were located either by first querying for popular key terms using each site's keyword query API (if available), or a ``top products'' query if available.  
For each such data record, two complexity metrics were computed: the \emph{average width}, corresponding to the number of properties, and \emph{average depth}, corresponding to the number of nested structures, of each record.  The third metric measured degree of overlap among sources in each category.  This was done by first mapping \emph{equivalent properties} between schemas, which was done manually by creating alignment tables for all properties of data sources in each category.  Each row comprised a property of a record of one data source, and all its closest matching properties from the others.  We used both property names and attribute descriptions (in documentation, if available) to make matching decisions.

@@

Once established, equivalent properties were examined firstly for naming inconsistencies.  Then, ignoring names, we examined whether the property's values were structurally compatible, defined as follows: if both values consisted of the same literal data type or had one or more equivalent subfields, they were considered compatible.  Finally, we examined incompatibilities not covered by naming or structural differences alone.  These \emph{modelling differences} arose from a variety of causes, including, but not limited to: measurement unit inconsistencies, measurement method (e.g., dew point vs relative humidity), differences in scale and granularity, and mismatches in what was being modelled (``offer'' versus ``listing'').\looseness=-1

>>>>

All of the participants used multiple web sites in order to complete their tasks, and all felt that the lack of existing integration between sites hindered their ability to make informed choices. Participants prioritised the sources they used by both the ease and immediacy of accessing them.  As a result, sources that took much effort or time to investigate were often excluded.

@@

\subsection{PS.2 - Technical Challenges of Data Integration}
Our analysis of structured data feeds started with identifying a set of candidate sources to examine.  We consulted the ProgrammableWeb API directory\footnote{ProgrammableWeb: \url{http://www.programmableweb.com/apis/directory}} list of most popular data feeds for this purpose.  To examine the many varieties of personal data sources, we selected from 5 categories: social network services, retailers, online event calendars, music sites, and weather, selecting 2--5 sources from each, for a total of 20.

For each source, 3--5 typical records of a particular type were obtained from each service's API or feed.  For social networking sites, user profiles were the type of record examined, while for retail sites, it was product information; for event tracking sites, we focused on event time/date information; for music sites, on song listing information; and for weather sites, forecast records were selected for our study.
%Records were located either by first querying for popular key terms using each site's keyword query API (if available), or a ``top products'' query if available.  
For each such data record, two complexity metrics were computed: the \emph{average width}, corresponding to the number of properties, and the \emph{average depth}, corresponding to the number of nested structures.  In addition, a third metric measured degree of overlap among the sources in each category.  This was accomplished by first mapping \emph{equivalent properties} between schemas, performed manually by creating alignment tables for all properties of data sources in each category.  Each row comprised a property of a record of one data source, and all its closest matching properties from the others.  We used both property names and attribute descriptions (in documentation, if available) to determine which properties were semantically equivalent.

@@

Once established, equivalent properties were examined, first, for naming inconsistencies.  Then, disregarding names, we examined whether the property's values were structurally compatible.  That is, if both values consisted of the same literal data type, or had one or more equivalent subfields, they were considered compatible.  Finally, we examined incompatibilities not covered by either naming or structural differences alone.  These \emph{modelling differences} arose from a variety of reasons, including, but not limited to, measurement unit inconsistencies, measurement method disagreements (e.g., dew point vs relative humidity), differences in scale and granularity, and mismatches in what was being modelled (``offer'' versus ``listing'').\looseness=-1
